---
title: "Biodiversity in the National Parks - Part II"
author: "Fisher Ankney"
date: "3/5/2018"
output: html_document
---


<br> 

```{r, message=FALSE}
library('tidyverse')
```
 
<br> 

```{r, message=FALSE}
parks <- read_csv('input/parks.csv')
species <- read_csv('input/species.csv')
```

```{r}
species_present <- species %>%
  filter(Occurrence == "Present")
```


<br> 

### What mammals are endangered?

```{r}
endangered <- species_present %>% 
  filter(Category == "Mammal" & `Conservation Status` == "Endangered") %>%
  select(`Common Names`) %>%
  unique()
print(endangered, n = 31)
```

<br> 

not done yet, data entry errors, get rid of doubles 
```{r}
endangered <- endangered[-c(1,4,9,13,18,23),]
print(endangered, n = 25)
```

<br> 

### Summary statistics on mammals in parks 

- max, min, median, standard deviation <br> 
- histogram, x axis = num of mammals, y axis = num of parks <br> 
```{r, warn=FALSE}
mammal_by_park <- species_present %>%
  filter(Category == "Mammal") %>% 
  group_by(`Park Name`) %>% 
  summarize(num_mammal = n())

ggplot(mammal_by_park) + 
  geom_bar(aes(num_mammal), binwidth = 5)
```

```{r}
range(mammal_by_park$num_mammal)

high_low <- mammal_by_park %>%
  arrange(num_mammal) 
high_low[c(1,56),]
  
median(mammal_by_park$num_mammal)

species_present %>% 
  filter(`Park Name` == "Dry Tortugas National Park" & Category == "Mammal") %>%
  select(`Common Names`)

sd(mammal_by_park$num_mammal)
```
<br> 

### Mammal thats in the most number of parks

```{r}
```
<br> 

### Are any mammal presense correlated?

<br> 

### Unulate case-study 


- the range of each of these mammals according to national park survey




